My Findings

### 2024-03-10 Findings (Shared Folder)/Chapters/PapersReviewed.tex
Updates from Overleaf

\section{Mathematical Modelling of Angiogenesis}{Chaplain}{2000, Journal of Neuro-Oncology}
discusses a variety of mathematical models used to describe capillary network formation, focusing on a model that generates 2D and 3D vascular structures. This model incorporates the migratory response of endothelial cells to tumor angiogenic factors, cell proliferation, and interactions with extracellular matrix macromolecules, among other factors \cite{Chaplain2000}

@@

reviews mathematical and computational models developed over two decades to study various aspects of angiogenesis. This work emphasizes the insights gained from these models in normal physiological growth, tumorigenesis, wound healing, and therapeutic strategy design \cite{Peirce2008}

@@

by Bookholt et al. (2016) introduces a 3D in vitro model simulating early stages of angiogenesis. The model addresses endothelial cell migration due to chemotaxis and durotaxis and includes various proteins impacting angiogenesis \cite{Bookholt2016}

\section{Mathematical modelling of dynamic adaptive tumour-induced angiogenesis: clinical implications and therapeutic targeting strategies}{S. McDougall, et. al.}{2006, Journal of theoretical biology}
presents a model that couples vessel growth with blood flow, offering insights into the adaptive and dynamic nature of tumor-induced angiogenesis and identifying new therapeutic targets for tumor management \cite{McDougall2006}

@@

provides a comprehensive review of mathematical models of angiogenesis in skin wound healing. It introduces the continuum reaction-transport framework as a useful tool for exploring unresolved questions in angiogenesis research \cite{Ghosh2015}

@@

\section{Simulating cancer growth with multiscale agent-based modeling.}{Zhihui Wang, et. al.}{2015, Seminars in cancer biology}
discuss the utility of ABMs in simulating diverse cancer behaviors, including tumor morphology, adaptation to the microenvironment, angiogenesis, and response to therapies. The review highlights the capability of ABMs to simulate the complex interplay between tumor cells and their microenvironment, paving the way for new therapeutic insights \cite{Wang2015}

@@

present an ABM that incorporates both stochastic and deterministic rules to simulate the initiation of sprouting angiogenesis. The model accurately simulates sprout initiation frequency and location, offering a deeper understanding of the balance between stochasticity and determinism in biological processes \cite{Walpole2015}

@@

develop an ABM to simulate vascular growth in engineered biomaterials, investigating the influence of growth factor release rate on angiogenesis. The model's results, validated against experimental studies, suggest microsphere properties that promote angiogenesis, offering insights into tissue engineering applications \cite{Bayrak2015}

\section{A cell-based model exhibiting branching and anastomosis during tumor-induced angiogenesis.}{A. Bauer, et. al.}{2007, Biophysical journal}
describe a cell-based ABM that integrates endothelial cell migration, growth, division, and the evolving structure of the stroma at the cellular Potts model level. The model successfully reproduces various morphologies of capillary sprouts observed in vivo, demonstrating the emergence of branching and anastomosis without prescribed rules \cite{Bauer2007a}

@@

developed a model that combines the processes of avascular tumor growth and the development of capillary networks through tumor-induced angiogenesis. This comprehensive model offers insights into the growth and development mechanisms of vascular tumors \cite{Cooper2010}

@@

presented an algorithm for constructing an arterial system model with physiologically significant geometric properties. Their analysis of the bifurcation exponent's effect on the arterial network's topology provides valuable insights into the optimal network topology for efficient vascular function  \cite{Kopylova2018}

@@

discuss a multidisciplinary approach combining experiments, image processing, analysis, and mathematical modeling focused on angiogenesis in the cornea micropocket assay. This approach aims to provide mechanistic insights into the action of angiogenic factors through quantitative data extraction and model parametrization \cite{Connor2015}

@@

\section{Consensus guidelines for the use and interpretation of angiogenesis assays}{Many authors}{2018, Angiogenesis}
published the first edition of consensus guidelines for the use and interpretation of angiogenesis assays. This collaborative work aims to serve as a reference for current and future angiogenesis research, promoting standardized methodologies across the field \cite{NowakSliwinska2018a}

\section{Zebrafish as an Emerging Model Organism to Study Angiogenesis in Development and Regeneration}{Myra N Chávez, et. al.}{2016, Front Physiol}
ocus on the zebrafish (Danio rerio) as an emerging model organism for studying angiogenesis in development and regeneration, highlighting its potential for understanding vascularization in artificial tissues and organs, as well as for drug discovery \cite{Chavez2016}

>>>>

\section{Mathematical Modelling of Angiogenesis}{Chaplain}{2000, Journal of Neuro-Oncology}
Discusses a variety of mathematical models used to describe capillary network formation, focusing on a model that generates 2D and 3D vascular structures. This model incorporates the migratory response of endothelial cells to tumor angiogenic factors, cell proliferation, and interactions with extracellular matrix macromolecules, among other factors \cite{Chaplain2000}

@@

Reviews mathematical and computational models developed over two decades to study various aspects of angiogenesis. This work emphasizes the insights gained from these models in normal physiological growth, tumorigenesis, wound healing, and therapeutic strategy design \cite{Peirce2008}

@@

By Bookholt et al. (2016) introduces a 3D in vitro model simulating early stages of angiogenesis. The model addresses endothelial cell migration due to chemotaxis and durotaxis and includes various proteins impacting angiogenesis \cite{Bookholt2016}

\section{Mathematical modelling of dynamic adaptive tumour-induced angiogenesis: clinical implications and therapeutic targeting strategies}{S. McDougall, et. al.}{2006, Journal of theoretical biology}
Presents a model that couples vessel growth with blood flow, offering insights into the adaptive and dynamic nature of tumor-induced angiogenesis and identifying new therapeutic targets for tumor management \cite{McDougall2006}

@@

Provides a comprehensive review of mathematical models of angiogenesis in skin wound healing. It introduces the continuum reaction-transport framework as a useful tool for exploring unresolved questions in angiogenesis research \cite{Ghosh2015}

@@

\section{Simulating cancer growth with multiscale agent-based modeling.}{Zhihui Wang, et. al.}{2015, Seminars in cancer biology}
Discusses the utility of ABMs in simulating diverse cancer behaviors, including tumor morphology, adaptation to the microenvironment, angiogenesis, and response to therapies. The review highlights the capability of ABMs to simulate the complex interplay between tumor cells and their microenvironment, paving the way for new therapeutic insights \cite{Wang2015}

@@

Presents an ABM that incorporates both stochastic and deterministic rules to simulate the initiation of sprouting angiogenesis. The model accurately simulates sprout initiation frequency and location, offering a deeper understanding of the balance between stochasticity and determinism in biological processes \cite{Walpole2015}

@@

Develops an ABM to simulate vascular growth in engineered biomaterials, investigating the influence of growth factor release rate on angiogenesis. The model's results, validated against experimental studies, suggest microsphere properties that promote angiogenesis, offering insights into tissue engineering applications \cite{Bayrak2015}

\section{A cell-based model exhibiting branching and anastomosis during tumor-induced angiogenesis.}{A. Bauer, et. al.}{2007, Biophysical journal}
Describes a cell-based ABM that integrates endothelial cell migration, growth, division, and the evolving structure of the stroma at the cellular Potts model level. The model successfully reproduces various morphologies of capillary sprouts observed in vivo, demonstrating the emergence of branching and anastomosis without prescribed rules \cite{Bauer2007a}

@@

Developed a model that combines the processes of avascular tumor growth and the development of capillary networks through tumor-induced angiogenesis. This comprehensive model offers insights into the growth and development mechanisms of vascular tumors \cite{Cooper2010}

@@

Presented an algorithm for constructing an arterial system model with physiologically significant geometric properties. Their analysis of the bifurcation exponent's effect on the arterial network's topology provides valuable insights into the optimal network topology for efficient vascular function  \cite{Kopylova2018}

@@

Discusses a multidisciplinary approach combining experiments, image processing, analysis, and mathematical modeling focused on angiogenesis in the cornea micropocket assay. This approach aims to provide mechanistic insights into the action of angiogenic factors through quantitative data extraction and model parametrization \cite{Connor2015}

@@

\section{Consensus guidelines for the use and interpretation of angiogenesis assays}{Many authors}{2018, Angiogenesis}
Published the first edition of consensus guidelines for the use and interpretation of angiogenesis assays. This collaborative work aims to serve as a reference for current and future angiogenesis research, promoting standardized methodologies across the field \cite{NowakSliwinska2018a}

\section{Zebrafish as an Emerging Model Organism to Study Angiogenesis in Development and Regeneration}{Myra N Chávez, et. al.}{2016, Front Physiol}
Focuses on the zebrafish (Danio rerio) as an emerging model organism for studying angiogenesis in development and regeneration, highlighting its potential for understanding vascularization in artificial tissues and organs, as well as for drug discovery \cite{Chavez2016}
